---
title: "Automatize Differential Expression for multiple contrasts"
author: "Lorena Pantano"
date: "`r Sys.Date()`"
output:
    html_document:
        df_print: paged
        highlight: tango
        number_sections: false
        self_contained: true
        theme: readable
        toc: true
        toc_float:
            collapsed: true
            smooth_scroll: false
---

# Parameters in header

If you look at the `de_template.Rmd`, there is a section with options that will change what file and options to use to run the DE analysis:

```
params:
    se_file: "data/se.rds"
    design: "~ type + condition"
    contrast: "condition.treated_vs_untreated,type.paired-end_vs_single-read"
    metadata: !r c("condition", "type") # first one used in some plots
    alpha: 0.05
    lfc: 0
    slot: "vst"
    output_dir: "."
    cache_dir: "../cache"
    cache_on: FALSE

```

Let's test this code. For that, we create a `test` folder.

```{r}
dir.create("test", showWarnings = FALSE)
```

These are the ones by default that works with a test data, if we try to run this with these options, it will fail:

```{r, eval=FALSE}
rmarkdown::render("de_template.Rmd", output_file = "test/de.html")
```


To have it working with our data, we need to change the options to match our data:

```{r}
rmarkdown::render("de_template.Rmd",
                  output_file = "test/de.html",
                  quiet = TRUE,
                  params = list(
                      se_file = "data/gse.rds",
                      design = "~ group",
                      contrast = "group.E_vs_D",
                      metadata = c("group"),
                      output_dir = "test"
                      
                  )
)
```


Look at `test/de.html`.


# Source

This template is available at [PILM public GitHub](https://github.com/pilm-bioinformatics/templates-rmd-de). You can download from there the `Rmd` file. 

[Go to homepage](https://pilm-bioinformatics.github.io/pilmbc211-rnaseq-ii/index.html)

*** 

*These materials have been developed by members of the teaching team at the [PILM - MIT Bioinformatics Core (PILMBC)](https://pilm-bioinformatics.github.io/knowledgebase). These are open access materials distributed under the terms of the [Creative Commons Attribution license](https://creativecommons.org/licenses/by/4.0/) (CC BY 4.0), which permits unrestricted use, distribution, and reproduction in any medium, provided the original author and source are credited.*

